## Bottom-up model

The bottom-up model starts with the results of the top-down regression to provide an estimate of the demand for energy in the buildings sector by fuel type and region.  Five interventions are then modelled to estimate the energy and emissions savings that result from: improved building fabric, increased use of ground-source heat pumps, improved efficiency of electrical appliances and lighting, switching of fuels from fossil to non-fossil sources, and decarbonization of the electricity grid.

```{r bottom-config}
## Read in the model components
##
## Each of these files contains named chunks which are then called below.
read_chunk('bottom-up-chunks.r')
```

```{r load-bottom-up-data}
```

```{r init-models}
```

### Residential space heat model

This model calculates demand for space heating in the residential based on emperically-observed relationships.  It therefore gives the percentage of residential energy demand for heat as a validation metric.
```{r run-space-heat-model}
```

### Ground source heat pumps
```{r run-gshp-model}
```

### Electrical appliance and lighting efficiency

```{r run-electrical-model}
```

### Fuel switching in space and water heating
```{r run-fuel-switch-model}
```

### Summary

Below is a summary of the energy and emission savings from all of these interventions.

```{r bottom-up-summary, fig.width=10}
```

Additionally there is an assumed change in the carbon intensity of the electricity used.

```{r emissions-calculation, fig.width=10}
```
```{r emissions-table, results='asis'}
```
