## Costing

We can now calculate the associated capital and operational costs associated with these technology changes.

```{r costing-config}
## Read in the model components
##
## Each of these files contains named chunks which are then called below.
read_chunk('costing-chunks.r')
```

### Capital costs

#### Space heating 
```{r space-heat-costs, results='asis'}
```

#### Heat pumps
```{r heat-pump-costs, results='asis'}
```

#### Electrical appliance and lighting efficiency
```{r efficiency-costs, results='asis'}
```

#### Other measures
```{r other-costs, results='asis'}
```

### Operationing and fuel costs
The only intervention with an explicit operating cost are the ground-source heat pumps.

```{r heat-pump-operating, results='asis'}
```

All of these interventions however, except for grid decarbonisation, incur changes in fuel consumption and this has cost implications.

```{r space-heating-fuels}
```

```{r gshp-fuels}
```

```{r fuel-switch-costs}
```

```{r efficiency-fuels}
```

### Summary

Now to summarize these costs, both in total and by household.

```{r cost-summary, results='asis', fig.width=14}
```

